Cover letter for ``Two applications\dots''

### 2021-03-07 papers/types2020/revisions/cultures.tex
Revisions to sections 2 and 3.  Added two references.

Gentzen's discovered that the key to treating classical and
intuitionistic logics in the same proof system was identifying the
structural rules of the weakening and contraction and
placing them on the right-side of sequents~\cite{gentzen35}.
This discovery lead him away from natural deduction to
multiple-conclusion sequent calculus, a very important kind of proof
system that has not been given a satisfactory representation in type
theory.  This same innovation of Gentzen's also opened the way to
another key proof-theoretic discovery, that of linear logic
\cite{girard87tcs}.  Similarly, sequent calculus provides an elegant
presentation of linear logic while most treatments of linear logic in
type theory have difficulty treating linear negation and the
multiplicative disjunction and its unit.

>>>>

%% DM Reviewer 1 want more references to claims made here.  I
%% lightened the claims and added two references.

Gentzen's discovered that the key to treating classical and
intuitionistic logics in the same proof system was identifying the
structural rules of the weakening and contraction and placing them on
the right-side of sequents~\cite{gentzen35}.  This discovery lead him
away from natural deduction to multiple-conclusion sequent calculus.
%
This same innovation of Gentzen's also opened the way to
another key proof-theoretic discovery, that of linear logic
and the linear negation~\cite{girard87tcs}.
%
While sequent calculus provides an elegant presentation of full linear
logic, most treatments of linear logic in type theory have
been limited to single-conclusion sequents~\cite{bierman95phd}
or to restricted, multiple-conclusion variants~\cite{hyland93apal}.

### 2021-03-07 papers/types2020/revisions/sec3.tex
Revisions to sections 2 and 3.  Added two references.

@@

In this and the next section, we shall only use a much reduced subset
of the FPC framework.  In particular, a proof certificate, denoted by
the schematic variable $\XXi$, is a particular term that is threaded
throughout a logic programming interperter.  For example, the
inference rules in Figure~\ref{fig:augmented} are augmented with an
additional premise that invokes an \emph{expert predicate} with is
responsible for extracting relevant information from a proof
certificate $\XXi$ as well as constructing continuation certificates,
such as, $\XXi_1$ and $\XXi_2$.  For example, the premise
$\prodE{\XXi}{\XXi_1}{\XXi_2}{t}$ calls the expert for products which
should extract from the certificate $\XXi$ a substitution term $t$ and
two continuation certificates $\XXi_1$ and $\XXi_2$ for the two
premises of this rule.  If the certificate $\XXi$ does not contain an
explicit substitution term, the expert predicate can simply return a
logic variable which would denote any term that satisfies subsequent
unification problems arising in completing the check of this
certificate.

>>>>

% DM I tried to down play FPC here so we would not need to say too
% much about the general picture.  Hopefully, the examples we provide
% and the few motivating sentences will make the reviewers happier.

@@

In this and the next section, we shall only use a much reduced subset
of the FPC framework: in essence, an FPC will be used as a simple
mechanism for bounding the search for proofs.  In our examples, a
proof certificate, denoted by the schematic variable $\XXi$, is a
particular term that is threaded throughout a logic programming
interperter.  For example, the inference rules in
Figure~\ref{fig:augmented} are augmented with an additional premise
that invokes an \emph{expert predicate} with is responsible for
extracting relevant information from a proof certificate $\XXi$ as
well as constructing continuation certificates, such as, $\XXi_1$ and
$\XXi_2$.  For example, the premise $\prodE{\XXi}{\XXi_1}{\XXi_2}{t}$
calls the expert for products which should extract from the
certificate $\XXi$ a substitution term $t$ and two continuation
certificates $\XXi_1$ and $\XXi_2$ for the two premises of this rule.
If the certificate $\XXi$ does not contain an explicit substitution
term, the expert predicate can simply return a logic variable which
would denote any term that satisfies subsequent unification problems
arising in completing the check of this certificate.
